Modelling BCG vaccination in the UK

### 2019-07-04 rmds/02-background.Rmd
shortened table and figure captions in lists

```{r tab-interventions, echo = FALSE, message = FALSE, dpi = 500}
tb_interventions_timeline %>% 
  set_names(c("Year",
              "Intervention",
              "Type",
              "Line",
              "Detail")) %>% 
  knitr::kable(caption = "A timeline of interventions against TB. Antibiotics used to treat TB are commonly given together, with those with the fewest side effects given first. Second line antibiotics are then used if the initial treatment fails or tests show the strain is multiply drug resistant. BCG - Bacillus Calmette–Guérin; TB – Tuberculosis; MRSA - Methicillin-resistant Staphylococcus aureus; DOTS - Directly Observed Treatment Short-course", booktabs = TRUE, longtable = TRUE, escape = FALSE) %>% 
  kable_styling(font_size = 8, latex_options = c("repeat_header")) %>% 
  column_spec(5, width = "10cm") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  landscape()
```

@@

```{r global-regional-tb-summary, fig.cap = "TB incidence rates (per 100,000) by region and globally from 2000 until 2017. Globally incidence rates have been declining since the early 2000's but this decline varies with region. Plot produced using getTBinR"}
plot_tb_burden_summary(conf = NULL, verbose = FALSE)
```

@@

```{r map-global-tb, fig.cap = "Global map of country level TB incidence rates (per 100,000 population) in 2017. Note the clustering of countries with high incidence rates in southern and central Africa and southern Asia. Map produced using getTBinR", fig.height = 5}
map_tb_burden(verbose = FALSE)
```

@@

```{r global-regional-mortality-summary, fig.cap = "TB mortality rates (per 100,000) by region and globally from 2000 until 2017. Mortality rates from TB have been falling in all regions since 2000. Plot produced using getTBinR"}
plot_tb_burden_summary(conf = NULL, verbose = FALSE, metric = "e_mort_100k", 
                       denom = "e_inc_num", facet = "Area", legend = "none", 
                       scales = "free_y") 
```

@@

```{r map-global-tb-with-hiv, fig.cap = "Global map of estimated HIV in incidence TB (percent) in 2017. Note that high percentage of TB cases with HIV in sub-saharan Africa. Map produced using getTBinR", fig.height = 5}
map_tb_burden(metric = "e_tbhiv_prct", verbose = FALSE)
```

@@

```{r map-global-tb-with-rr, fig.cap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017. Not that a far higher percentage of TB cases have rifampicin resistance in the former Soviet Union that in the rest of the world. Map produced using getTBinR (see \\@ref(getTBinR) for details)", fig.height = 5}
map_tb_burden(metric = "e_rr_pct_new", verbose = FALSE)
```

```{r prop-rr-with-mdr-tab, warning = FALSE}
summarise_tb_burden(countries = "Russia", 
                    metric = "e_mdr_pct_rr_new", verbose = FALSE,
                    year = 2017, stat = "median") %>% 
  mutate_at(.vars = c("e_mdr_pct_rr_new", "e_mdr_pct_rr_new_lo", "e_mdr_pct_rr_new_hi"),
            funs(ifelse(. > 100, 100, .))) %>% 
  mutate(`Median percentage of RR* cases with MDR** (95% IQR***)` = 
           pretty_ci(e_mdr_pct_rr_new,
                     e_mdr_pct_rr_new_lo, 
                     e_mdr_pct_rr_new_hi)) %>% 
  mutate(`Median Proportion of RR* cases with MDR** (95% IQR***)` = 
           ifelse(area == "Russian Federation", paste(pretty_round(e_mdr_pct_rr_new), "***"),
                  as.character(`Median percentage of RR* cases with MDR** (95% IQR***)`)
                  )) %>% 
  select(Area = area, `Median percentage of RR* cases with MDR** (95% IQR***)`) %>% 
  knitr::kable(caption = "Percentage (\\%) of rifampicin resistant TB cases that have multi-drug resistant TB in Russia and regional medians, with interquartile ranges.",
        booktabs = TRUE) %>% 
  add_footnote(label = c("* Rifampicin resistance", "** Multi-Drug Resistant TB", "*** Interquartile Range"), notation = "none") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  {.}
```

@@

```{r plot-incidence, echo = FALSE, warning = FALSE, message = FALSE, dpi = 300, fig.height = 10, fig.width = 10, fig.cap = "TB notifications in England and Wales from 1913 to 2017, stratified initially by respiratory/non-respiratory status and from 1982 by pulmonary/non-pulmonary TB. Interventions are highlighted with vertical lines, with linetype denoting the type of intervention, more information on each intervention is available in the corresponding table. Figure produced using tbinenglanddataclean (https://www.samabbott.co.uk/tbinenglanddataclean/)"}
plot_historic_tb_ew() + theme(legend.position = "top")
```

@@

```{r plot-prop-pul, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300, fig.height = 10, fig.width = 10, fig.cap = "From 1913 until 1981 the figure shows the proportion respiratory vs. non-respiratory cases and from 1982 it shows the proportion of pulmonary vs. non-pulmonary TB. Figure produced using tbinenglanddataclean (https://www.samabbott.co.uk/tbinenglanddataclean/)"}
plot_historic_prop_pul_tb() + theme(legend.position = "top")
```

>>>>

```{r tab-interventions, echo = FALSE, message = FALSE, dpi = 500}
tb_interventions_timeline %>% 
  set_names(c("Year",
              "Intervention",
              "Type",
              "Line",
              "Detail")) %>% 
  knitr::kable(
    caption.short = "A timeline of interventions against TB",
    caption = "A timeline of interventions against TB. Antibiotics used to treat TB are commonly given together, with those with the fewest side effects given first. Second line antibiotics are then used if the initial treatment fails or tests show the strain is multiply drug resistant. BCG - Bacillus Calmette–Guérin; TB – Tuberculosis; MRSA - Methicillin-resistant Staphylococcus aureus; DOTS - Directly Observed Treatment Short-course", booktabs = TRUE, longtable = TRUE, escape = FALSE) %>% 
  kable_styling(font_size = 8, latex_options = c("repeat_header")) %>% 
  column_spec(5, width = "10cm") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  landscape()
```

@@

```{r global-regional-tb-summary, fig.cap = "TB incidence rates (per 100,000) by region and globally from 2000 until 2017. Globally incidence rates have been declining since the early 2000's but this decline varies with region. Plot produced using getTBinR", fig.scap = "TB incidence rates (per 100,000) by region and globally from 2000 until 2017.", out.extra = ""}
plot_tb_burden_summary(conf = NULL, verbose = FALSE)
```

@@

```{r map-global-tb, fig.cap = "Global map of country level TB incidence rates (per 100,000 population) in 2017. Note the clustering of countries with high incidence rates in southern and central Africa and southern Asia. Map produced using getTBinR", fig.scap = "Global map of country level TB incidence rates (per 100,000 population) in 201", fig.height = 5}
map_tb_burden(verbose = FALSE)
```

@@

```{r global-regional-mortality-summary, fig.scap =  "TB mortality rates (per 100,000) by region and globally from 2000 until 2017.", fig.cap = "TB mortality rates (per 100,000) by region and globally from 2000 until 2017. Mortality rates from TB have been falling in all regions since 2000. Plot produced using getTBinR", out.extra = ""}
plot_tb_burden_summary(conf = NULL, verbose = FALSE, metric = "e_mort_100k", 
                       denom = "e_inc_num", facet = "Area", legend = "none", 
                       scales = "free_y") 
```

@@

```{r map-global-tb-with-hiv, fig.scap = "Global map of estimated HIV in incidence TB (percent) in 2017.", fig.cap = "Global map of estimated HIV in incidence TB (percent) in 2017. Note that high percentage of TB cases with HIV in sub-saharan Africa. Map produced using getTBinR", fig.height = 5}
map_tb_burden(metric = "e_tbhiv_prct", verbose = FALSE)
```

@@

```{r map-global-tb-with-rr, fig.scap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017.", fig.cap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017. Not that a far higher percentage of TB cases have rifampicin resistance in the former Soviet Union that in the rest of the world. Map produced using getTBinR (see \\@ref(getTBinR) for details)", fig.height = 5}
map_tb_burden(metric = "e_rr_pct_new", verbose = FALSE)
```

```{r prop-rr-with-mdr-tab, warning = FALSE}
summarise_tb_burden(countries = "Russia", 
                    metric = "e_mdr_pct_rr_new", verbose = FALSE,
                    year = 2017, stat = "median") %>% 
  mutate_at(.vars = c("e_mdr_pct_rr_new", "e_mdr_pct_rr_new_lo", "e_mdr_pct_rr_new_hi"),
            funs(ifelse(. > 100, 100, .))) %>% 
  mutate(`Median percentage of RR* cases with MDR** (95% IQR***)` = 
           pretty_ci(e_mdr_pct_rr_new,
                     e_mdr_pct_rr_new_lo, 
                     e_mdr_pct_rr_new_hi)) %>% 
  mutate(`Median Proportion of RR* cases with MDR** (95% IQR***)` = 
           ifelse(area == "Russian Federation", paste(pretty_round(e_mdr_pct_rr_new), "***"),
                  as.character(`Median percentage of RR* cases with MDR** (95% IQR***)`)
                  )) %>% 
  select(Area = area, `Median percentage of RR* cases with MDR** (95% IQR***)`) %>% 
  knitr::kable(
               caption = "Percentage (\\%) of rifampicin resistant TB cases that have multi-drug resistant TB in Russia and regional medians, with interquartile ranges.",
        booktabs = TRUE) %>% 
  add_footnote(label = c("* Rifampicin resistance", "** Multi-Drug Resistant TB", "*** Interquartile Range"), notation = "none") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  {.}
```

@@

```{r plot-incidence, echo = FALSE, warning = FALSE, message = FALSE, dpi = 300, fig.height = 10, fig.width = 10, fig.scap = "TB notifications in England and Wales from 1913 to 2017, stratified initially by respiratory/non-respiratory status and from 1982 by pulmonary/non-pulmonary TB.", fig.cap = "TB notifications in England and Wales from 1913 to 2017, stratified initially by respiratory/non-respiratory status and from 1982 by pulmonary/non-pulmonary TB. Interventions are highlighted with vertical lines, with linetype denoting the type of intervention, more information on each intervention is available in the corresponding table. Figure produced using tbinenglanddataclean (https://www.samabbott.co.uk/tbinenglanddataclean/)", out.extra = ""}
plot_historic_tb_ew() + theme(legend.position = "top")
```

@@

```{r plot-prop-pul, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300, fig.height = 10, fig.width = 10, fig.scap = "From 1913 until 1981 the figure shows the proportion respiratory vs. non-respiratory cases and from 1982 it shows the proportion of pulmonary vs. non-pulmonary TB.", fig.cap = "From 1913 until 1981 the figure shows the proportion respiratory vs. non-respiratory cases and from 1982 it shows the proportion of pulmonary vs. non-pulmonary TB. Figure produced using tbinenglanddataclean (https://www.samabbott.co.uk/tbinenglanddataclean/)"}
plot_historic_prop_pul_tb() + theme(legend.position = "top")
```

### 2019-07-04 rmds/03-getTBinR.Rmd
shortened table and figure captions in lists

```{r map-tb-incidence-eur, fig.cap = "Map of global TB incidence rates in 2017 as generated by `getTBinR'. Visualising the data with a map allows for spatial trends to be rapidly explored.", echo = TRUE}
map_tb_burden(metric = "e_inc_100k", verbose = FALSE)
```

@@

```{r plot-regional-summary, fig.cap = "TB incidence by region and globally as computed and visualised by `getTBinR`. Confidence intervals have been disabled in order to avoid obscuring the dominant trends.", echo = TRUE} 
plot_tb_burden_summary(conf = NULL, metric_label = "e_inc_100k",
                       verbose = FALSE)
```

@@

```{r plot-tb-burden, fig.cap = "TB incidence rates over time, with confidence intervals, in the UK. As produced by `getTBinR`.", echo = TRUE}
plot_tb_burden(metric = "e_inc_100k",
               countries = "United Kingdom",
               verbose = FALSE) 
```

@@

```{r report-snapshot, echo = FALSE, fig.cap = "Screenshot of the start of the built in package summary report, for the United Kingdom."}
knitr::include_graphics(file.path(resources_path, "img", "ExampleCountryReport.png"))
```

>>>>

```{r map-tb-incidence-eur, fig.scap = "Map of global TB incidence rates in 2017 as generated by `getTBinR'.", fig.cap = "Map of global TB incidence rates in 2017 as generated by `getTBinR'. Visualising the data with a map allows for spatial trends to be rapidly explored.", echo = TRUE, out.extra = ""}
map_tb_burden(metric = "e_inc_100k", verbose = FALSE)
```

@@

```{r plot-regional-summary, fig.scap = "TB incidence by region and globally as computed and visualised by `getTBinR`.", fig.cap = "TB incidence by region and globally as computed and visualised by `getTBinR`. Confidence intervals have been disabled in order to avoid obscuring the dominant trends.", echo = TRUE, out.extra = ""} 
plot_tb_burden_summary(conf = NULL, metric_label = "e_inc_100k",
                       verbose = FALSE)
```

@@

```{r plot-tb-burden, fig.scap = "TB incidence rates over time, with confidence intervals, in the UK. As produced by `getTBinR`.", fig.cap = "TB incidence rates over time, with confidence intervals, in the UK. As produced by `getTBinR`.", echo = TRUE, out.extra = ""}
plot_tb_burden(metric = "e_inc_100k",
               countries = "United Kingdom",
               verbose = FALSE) 
```

@@

```{r report-snapshot, echo = FALSE, fig.cap = "Screenshot of the start of the built-in package summary report, for the United Kingdom."}
knitr::include_graphics(file.path(resources_path, "img", "ExampleCountryReport.png"))
```
